\documentclass{letter}

\usepackage{geometry}

\geometry{a4paper, margin=1.5in}

\signature{Siobhán Sterrett [she/her] \\ siobhan.sterrett@gmail.com \\ 917.938.4820}

\begin{document}

\begin{letter}{}

\opening{To Whom It May Concern:}

I am a software engineer with six years of experience working in a number of different areas. I am applying for a
  position with ButterflyMX as an Embedded Systems Application Developer because I believe that my particular experience
  and expertise will be of great benefit to the company and to your customers, and that ButterflyMX will in turn provide
  me with opportunities to grow as a developer.

I have extensive experience with building concurrent embedded applications, working closely alongside hardware engineers
  and subject-matter experts, and creating secure and efficient systems for the benefit of non-technical end users. I
  know that user experience is paramount, and that even when engineering isn't a ``customer-facing'' position, we still
  make decisions that directly impact our customers. I have made it my goal to find potential problems \emph{before}
  customers or users notice them, and fix them so that they stay fixed.

Although I have not yet had the opportunity to work with video or audio codecs or with streaming protocols in a
  professional setting, my personal work has given me some experience. I hope to learn more about this field, so I can
  leverage my abstract technical understanding to build concrete, fault-tolerant, and secure systems. I am glad to know
  that teamwork is a value held by the company; I'm sure that I will have much to learn, and that I will have much to
  offer my teammates in return.

I am curious to hear more about how ButterflyMX is using Go and Python for its embedded systems. I have used Python
  extensively in previous positions, both as a scripting language and for application development, but for embedded
  applications it has been my wont to use langauges like C++ or Rust, which are more efficient and which have far less
  runtime overhead. I look forward to learning more about your processes, and the decisions which have led the team to
  where it is today.

It is my hope that we will get to work together soon.

\closing{Yours,}

\end{letter}

\end{document}
